\section{Purpose}
% Syftet specificerar vad projektet är tänkt att resultera i och vilken typ av resultat som kommer att uppnås. Ett projekt kan ha flera syften som är relaterade till de ämnen/problem som presenteras i bakgrunden. I de flesta fall är det dock lämpligt att ha endast ett generellt syfte, som sedan bryts ner i mer detaljerade delar längre fram i kandidatarbetets process och uppsats/rapport.

\subsection{Educational goals}
The project's purpose is to build a quantum computer simulator that works as an aid for high school and college level students to be able to simulate and learn about how a working quantum computer functions. The tool will have features that enables the user to build their own quantum circuits through a drag and drop system as well as a time slider that moves the qubits through the circuit and visualizes the quantum state of the system. The learning objectives intended with the tool is an enhanced understanding of quantum mechanical concepts such as quantum entanglement, quantum teleportation as well as the basic functionality and possibilities of quantum computers.

\subsection{Bridging the Gap}
Most existing quantum computer simulation tools today are focused towards research purposes and towards people with a strong existing understanding of quantum computing. 
By providing an alternative tool with a low requirement for users, more people can interact with it and increase the number of people interested in the subject. This is done with an interactive design and simple visualizations with explanations that enables anyone to experiment with a quantum computer.

\subsection{Enhancing Intuition}
One of the key parts and more difficult concepts for beginners is entanglement. With a tool that allows users to manipulate  time and seeing the cause and effect of entanglement, the tool builds a more intuitive understanding of this phenomenon. This also applies to other parts such as the behavior of different quantum gates and qubits when they interact with each other and how measuring a qubit can change the state of the entire system.
